% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2010 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

%
% Update on: 
%   - Overleaf
%   - Github repo: resume


\documentclass[legalpaper,10pt]{article}
\usepackage[T1]{fontenc}
\usepackage{charter}
%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\definecolor{mygrey}{gray}{0.80}
\usepackage{hyperref} 

\usepackage{xcolor}
\hypersetup{
	colorlinks,
	linkcolor={red!50!black},
	citecolor={blue!50!black},
	urlcolor={blue!80!black}
}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
%\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}

\newcommand{\ressubheading}[4]{
	\begin{tabular*}{7.1in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textit{#4} \\
	\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubheadinged}[4]{
	\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4}\\
	\end{tabular*}\vspace{-6pt}}

%-----------------------------------------------------------


\begin{document}

	\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}}
		\\
		\\
		\\
		\textbf{\large Sourav Majumder}\\
		\\
		Dhaka, Bangladesh, \href{mailto:sourav.cse18.duet@gmail.com}{sourav.cse18.duet@gmail.com}, +880-1863599784, \textbf{Github}: \href{https://github.com/s0urav6529}{@s0urav6529}, LinkedIn: \href{https://www.linkedin.com/in/s0urav6529/}{@s0urav6529} 
		\\
		\\
		I am a tech enthusiast,a \textbf{problem solver} and always love to solve problems.         Day by day learning new things and gathering \\ experiences. I am always
            passionate about my goal.
	\end{tabular*}
	
	\vspace{0.25in}
	
	\resheading{Education}
	\begin{itemize}
	    \vspace{0.10in}
		\item \ressubheading{Dhaka University of Engineering \& Technology, Gazipur}{}{}{ 2019 -  2023}
		\begin{itemize}
			\item BSc, Computer Science and Engineering.
                \item CGPA - \textbf{3.71}
		\end{itemize}

            \item \ressubheading{Chittagong Polytechnic Institute, Chittagong}{}{}{2014 - 2018}
		\begin{itemize}
			\item Diploma in Engineering, Computer Technology.
                \item CGPA - \textbf{3.57}
		\end{itemize}
	
	\end{itemize}
	
	\vspace{0.25in}
	
	\resheading{Technical Skills}
        \begin{itemize}  
            \vspace{0.10in}
            \item \ressubheading{Programming Language}{}{}{}
		\begin{itemize}
			\item C, C++(Advanced), Java, Python.
		\end{itemize}

            \item \ressubheading{Problem Solving}{}{}{}
		\begin{itemize}
                \item Almost (\href{https://www.stopstalk.com/user/profile/Sourav_sCodes}{ 2200+ and  counting}) problems solved on several online platform.
			\item Codeforces Max-rating \textbf{1421}. Handle:           \href{https://codeforces.com/profile/s0urav6529}{@s0urav6529} 
                \item Codechef Max-rating \textbf{1671}. Handle: \href{https://www.codechef.com/users/codepro16}{@codepro16} 
		\end{itemize}

            \item \ressubheading{Projects}{}{}{}
		\begin{itemize}
                \item \textbf{SuperShop Management} (Used javaSwing, javascript and mysql.It was a project of a super shop where the cashier can easily handle incoming-outgoing activity of the shop in one handed)
		\end{itemize}
            \begin{itemize}
                \item \textbf{Online library Manager} (Used C\# and mysql. A library manager that can maintain libraries daily workout vai online.)
		\end{itemize}
	\end{itemize}

	\vspace{0.25in}

        \resheading{Competitive Programming Experiences}
	\begin{itemize}
            \vspace{0.10in}
            \item \ressubheading{ICPC Asia West Continent Finalist 2021}{}{}{}
            \begin{itemize}
		    \item Was first International onsite contest.Our team attended as the \textbf{19'th} team from our country.
		\end{itemize}
             \item \ressubheading{ICPC Asia Dhaka Regional Contest 2021}{}{}{}
             \begin{itemize}
		    \item  Selected for ICPC Asia Dhaka Regional 2021 hosted by BUBT and secured \textbf{40'th} rank among \textbf{165} teams.
		\end{itemize}
            \item \ressubheading{Inter University Programming Contest}{}{}{}
             \begin{itemize}
		    \item BUET IUPC 2022 - BUET ,  RUET IUPC 2022 - RUET , AUST IUPC 2022 - AUST.
		\end{itemize}
  
            \item \ressubheading{Intra DUET Programming Contest}{}{}{}
             \begin{itemize}
		    \item IDPC-2021, IDPC-2022, IDPC-2023.
		\end{itemize}
            
	\end{itemize}

        \vspace{0.25in}
	
	\resheading{Leadership Experiences (selected)}
	\begin{itemize}
            \vspace{0.10in}
            \item \ressubheading{Class Representative (CR)}{}{}{}
		\begin{itemize}
		    \item Was class representative at 4th year and 1st semester. Collaboration with            teachers, lead the students was a great experience indeed.
		\end{itemize}
            
		\item \ressubheading{Programming and Algorithms Secretary - DUET Computer Society}{}{}{ 2022 -  2023}
		\begin{itemize}
		    \item As a member of DUET computer society committee sheared programming knowledge 
                and organizing online training contest (\href{https://toph.co/contests/training/6c3m3hu}{ problem setter}). 
		\end{itemize}
		
		\item \ressubheading{Vice President - DUET Sports Club}{}{}{ 2022 -  2023}
		\begin{itemize}
		    \item Organized several inter-department Cricket and Football tournaments, learned how tough it is to finish a sports tournament in a chaotic setting like South Asia.
		\end{itemize}
		
	\end{itemize}

	\vspace{0.25in}
 
	\resheading{Awards and Certifications}
	\begin{itemize}
            \vspace{0.10in}
	
		\item \textbf{Champion of Intra-DUET Programming Contest} (2022, Became the \href{https://toph.co/contests/training/nmp8c7a/standings}{ \textbf{champion}} of Intra-DUET Programming Contest held by DUET Computer Society, DUET)
		
		\item \textbf{2nd Runner-Up of Intra-DUET Programming Contest} (2023, Became the \href{https://toph.co/contests/training/bvmhmvn/standings}{ \textbf{2nd Runner-Up}} of Intra-DUET Programming Contest held by DUET Computer Society, DUET)

        \item \textbf{Sports} (Inter-Department Football Tournament 2022, \textbf{Champion}, Inter-Hall Volleyball Tournament 2022, \textbf{Runner-Up}, Intra-Hall Badminton Tournament 2023, \textbf{Runner Up}, Intra-CSE Cricket Tournament 2022, \textbf{Champion})

	\end{itemize}

	\vspace{0.20in}
	
	\resheading{Field of Interests}
            \vspace{0.10in}
		\begin{itemize}
			\item Software development, Data Structure, problem solving,  mathematics, Machine Learning , Artificial Intelligence, Computer system, Educational psychology, Sports, poetry writing and anything that stirs the intellectual interest.
		\end{itemize}

\end{document}
